---
title: "p8105_hw5_bl2898"
author: "Boqian Li"
date: "11/19/2021"
output: html_document
---

## Problem 0

This “problem” focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files. To that end:

```{r}
library(tidyverse)
```

## Problem 1 

For this problem, we are interested in data gathered and made public by _The Washington Post_ on homicide in 50 large U.S. cities. The code chunk below imports and clean data.

```{r}
homicide_df = 
  read_csv("homicide-data.csv", na = c("", "unknown")) %>% 
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved",
         )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsoAL")
```

Let's focus on Baltimore, MD. 

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

prop.test(
  x = balmore_summary %>% pull(unsolved), 
  n = balmore_summary %>% pull(n) 
  )

baltimore_test %>% 
  broom::tidy()
```

```{r}
prop_test_function = function(city_df){
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n))
  
  return(city_test)
}

prop_test_function(baltomore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```



```{r}
homicide_df
```

